---
title: "Ex 6 - Linear and Logistic Regression"
author: "V.P.B. Sree Nilan"
date: "`r Sys.Date()`"
output: pdf_document
geometry:
  left=0.75in,right=0.5in,top=0.5in,bottom=0.5in
fontsize: 10pt
spacing: single
fig_caption: yes
indent: true
vspace: -1cm
header-includes: "\\setlength{\\columnsep}{8pt} - p{0.5\\linewidth}}"
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### 1. Write a R program to do the Linear/Logistic regression with random data points.

```{r}
(x <- round(runif(10, min = 300, max = 1000)))
(y <- runif(10, min = 1, max = 2))
data <- data.frame(x,y)
model <- lm(y ~ x,data =data)
model
n_data <- data.frame(x = c(823))
pred <- predict(model,newdata=n_data)
cat("Prediction : ", pred, "\n")
e <- y - pred
cat("Error : ", e, "\n")
rmse <- sqrt(sum(e*e))
cat("Root Mean Square Error : ", rmse)
```

### 2. Write a R program to do Linear/Logistic regression for the given California_housing dataset using API

```{r}
print("Linear Regression")
library(readr)
housing <- read_csv("D:\\Nilan\\housing.csv", show_col_types = FALSE)
head(housing)
train_indices <- sample(1:nrow(housing), 0.7*nrow(housing))
train_data <- housing[train_indices,]
test_data <- housing[-train_indices,]
model <- lm(median_house_value ~ longitude + latitude + housing_median_age + total_rooms + total_bedrooms + population + households ++median_income + ocean_proximity, data = train_data)
coefficients(model)
pred <- predict(model, test_data)
suppressWarnings(e <- train_data$median_income - pred)
rmse<-sqrt(sum(e * e))
cat("Root Mean Square Error : ", rmse, "\n")
```

```{r}
print("Logistic Regression")
library(readr)
housing <- read_csv("D:\\Nilan\\housing.csv", show_col_types = FALSE)
head(housing)
train_indices <- sample(1:nrow(housing), 0.7*nrow(housing))
train_data <- housing[train_indices,]
test_data <- housing[-train_indices,]
model <- glm(median_house_value ~ longitude + latitude + housing_median_age + total_rooms + total_bedrooms + population + households ++median_income + ocean_proximity, data = train_data)
coefficients(model)
pred<-predict(model, test_data)
head(pred)
suppressWarnings(e<-train_data$median_income - pred)
head(e)
rmse<-sqrt(sum(e*e))
cat("Root Mean Square Error:", rmse, "\n")
```

### 3. Write a R program to do the Linear/Logistic regression with random data points without APIs

```{r}
(x <- round(runif(10, min = 300, max = 1000)))
(y <- runif(10, min = 1, max = 2))
xb<-mean(x)#mean of x
yb<-mean(y)#mean of y
n<-length(y) #length of y
x2<-x*x # x square
xy<-x*y # x*y value
sxy<-sum(xy)
x3<-xb*xb # xb square
sx2<-sum(x2)
a<-(sxy-(n*xb*yb))
b<-(sx2-(n*x3))
m<-(a/b)
cat("slope:",m,"\n")
c<-yb-m*xb
cat("intercept:",c,"\n")
yp<-m*823+c
cat("prediction:",yp,"\n")
e<-y-yp
cat("error:",e,"\n")
mse<-sum(e*e)
cat("mean square error:",mse,"\n")
rmse<-sum(sqrt(mse))
cat("root mean square error:",rmse,"\n")
```

### 4. Consider a company comprised a sample of 1000 customers. We need to predict the probability whether a customer will buy (y) a particular magazine or not. Use logistic regression.

```{r}
n_obs <- 1000
cust_inco<-sample(15000:30000,n_obs, replace = TRUE)
interest <- sample(c("yes", "No"), n_obs, replace = TRUE)
rating <- sample(1:5, n_obs, replace = TRUE)
buy_or_not <- sample(c("1", "0"), n_obs, replace = TRUE)
gender <- sample(c("Male", "Female"), n_obs, replace = TRUE)
age <- sample(20:35, n_obs, replace = TRUE)

# Combine data into a dataframe
synthetic_data <- data.frame(
  INCOME=cust_inco ,
  Age = age,
  INTEREST = interest,
  GENDER = gender,
  RATING = rating,
  BUY_OR_NOT = buy_or_not
)
head(synthetic_data)
train_indices<-sample(1:nrow(synthetic_data),0.7*nrow(synthetic_data))
train_data<-synthetic_data[train_indices,]
test_data<-synthetic_data[-train_indices,]
model1<-glm(buy_or_not ~ income,data=train_data)
coefficients(model1)
pred<-predict(model1,test_data)
```

####Write a program to predict diabetes Pima Indian Diabetes dataset
using Logistic Regression Classifier.

```{r}
library(readr)
diabetes <- read_csv("diabetes.csv")
head(diabetes)
colnames(diabetes)
train_indices<-sample(1:nrow(diabetes),0.7*nrow(diabetes))
train_data<-diabetes[train_indices,]
test_data<-diabetes[-train_indices,]
model<-lm(Outcome ~ Pregnancies+Glucose+BloodPressure+SkinThickness+Insulin+BMI+DiabetesPedigreeFunction+Age  ,data=train_data)
coefficients(model)
pred<-predict(model,test_data)
#head(pred)
cat("prediction:",pred,"\n")
#e<-train_data$Outcome-pred
#head(e)
#cat("error:",e,"\n")
rmse<-sqrt(sum(e*e))
cat("root mean square error:",rmse,"\n")
```

```{r}
library(readr)
diabetes <- read_csv("diabetes.csv")
head(diabetes)
colnames(diabetes)
train_indices<-sample(1:nrow(diabetes),0.7*nrow(diabetes))
train_data<-diabetes[train_indices,]
test_data<-diabetes[-train_indices,]
model<-glm(Outcome ~ Pregnancies+Glucose+BloodPressure+SkinThickness+Insulin+BMI+DiabetesPedigreeFunction+Age  ,data=train_data)
coefficients(model)
pred<-predict(model,test_data)
head(pred)
cat("prediction:",pred,"\n")
e<-train_data$Outcome-pred
#head(e)
#cat("error:",e,"\n")
rmse<-sqrt(sum(e*e))
cat("root mean square error:",rmse,"\n")
```

6.  Write a program to predict whether the client will subscribe (1/0)
    to a term deposit (variable y). The dataset comes from the UCI
    Machine Learning repository, and it is related to direct marketing
    campaigns (phone calls) of a Portuguese banking institution.

    ```{r}
    bank_data <- data.frame(
      age = rnorm(1000, mean = 40, sd = 10),
      job = sample(c("management", "blue-collar", "technician", "admin."), 1000, replace = TRUE),
      marital = sample(c("married", "single", "divorced"), 1000, replace = TRUE),
      education = sample(c("primary", "secondary", "tertiary"), 1000, replace = TRUE),
      balance = rnorm(1000, mean = 5000, sd = 10000),
      subscription = sample(c(0, 1), 1000, replace = TRUE)
    )

    # Fit logistic regression model
    logit_model_bank <- glm(subscription ~ ., data = bank_data, family = binomial)

    # Model summary
    summary(logit_model_bank)

    bank_data$predicted_probability <- predict(logit_model_bank, newdata = bank_data, type = "response")

    # View the predicted probabilities
    head(bank_data$predicted_probability)

    ```
